Creating optimal conditions for reproducible data analysis in \R with `fertile'\protect\thanks{The authors gratefully acknowledge contributions from Hadley Wickham, Jenny Bryan, Greg Wilson, Edgar Ruiz, and other members of the \pkg{tidyverse} team.}

### 2020-10-11 STAT-paper-template/APA/fertile.tex
back to original tex file (not hard coded)

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# -- Compiling... -------------------------- fertile 0.0.0.9028 --}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# -- Rendering R scripts... ---------------- fertile 0.0.0.9028 --}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# Error in eval\_tidy(xs[[j]], mask): object '.Random.seed' not found}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# -- Running reproducibility checks -------- fertile 0.0.0.9028 --}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# -- Rendering R scripts... ---------------- fertile 0.0.0.9028 --}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in eval\_tidy(xs[[j]], mask): object '.Random.seed' not found}}\end{kframe}
\end{knitrout}

@@

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# -- Rendering R scripts... ---------------- fertile 0.0.0.9028 --}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in eval\_tidy(xs[[j]], mask): object '.Random.seed' not found}}\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{log_report}\hlstd{()}
\end{alltt}
\begin{verbatim}
## # A tibble: 3 x 4
##   path         path_abs                             func     timestamp          
##   <chr>        <chr>                                <chr>    <dttm>             
## 1 package:pur~ <NA>                                 base::l~ 2020-10-10 00:39:23
## 2 package:for~ <NA>                                 base::l~ 2020-10-10 00:39:23
## 3 project_mic~ /Users/audreybertin/Documents/ferti~ readr::~ 2020-10-10 00:39:23
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{fertile}\hlopt{::}\hlstd{read_csv}
\end{alltt}
\begin{verbatim}
## function(file, ...) {
##   if (interactive_log_on()) {
##     log_push(file, "readr::read_csv")
##     check_path_safe(file, ... = "readr::read_csv")
##     readr::read_csv(file, ...)
##   }
## }
## <bytecode: 0x7fcede54ad08>
## <environment: namespace:fertile>
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{proj_dir}
\end{alltt}
\begin{verbatim}
## [1] "project_miceps"
\end{verbatim}
\begin{alltt}
\hlstd{fs}\hlopt{::}\hlkwd{dir_ls}\hlstd{(proj_dir)} \hlopt{%>%} \hlkwd{head}\hlstd{(}\hlnum{3}\hlstd{)}
\end{alltt}
\begin{verbatim}
## project_miceps/Blot_data_updated.csv   project_miceps/CS_data_redone.csv      
## project_miceps/Estrogen_Receptors.docx
\end{verbatim}
\begin{alltt}
\hlstd{temp_dir} \hlkwb{<-} \hlkwd{sandbox}\hlstd{(proj_dir)}
\hlstd{temp_dir}
\end{alltt}
\begin{verbatim}
## /var/folders/v6/f62qz88s0sd5n3yqw9d8sb300000gn/T/RtmpNAq0UZ/project_miceps
\end{verbatim}
\begin{alltt}
\hlstd{fs}\hlopt{::}\hlkwd{dir_ls}\hlstd{(temp_dir)} \hlopt{%>%} \hlkwd{head}\hlstd{(}\hlnum{3}\hlstd{)}
\end{alltt}
\begin{verbatim}
## /var/folders/v6/f62qz88s0sd5n3yqw9d8sb300000gn/T/RtmpNAq0UZ/project_miceps/Blot_data_updated.csv
## /var/folders/v6/f62qz88s0sd5n3yqw9d8sb300000gn/T/RtmpNAq0UZ/project_miceps/CS_data_redone.csv
## /var/folders/v6/f62qz88s0sd5n3yqw9d8sb300000gn/T/RtmpNAq0UZ/project_miceps/Estrogen_Receptors.docx
\end{verbatim}
\end{kframe}
\end{knitrout}

>>>>

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# -- Compiling... ------------------------------------------------------------ fertile 0.0.0.9028 --}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# -- Rendering R scripts... -------------------------------------------------- fertile 0.0.0.9028 --}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# -- Running reproducibility checks ------------------------------------------ fertile 0.0.0.9028 --}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# v Checking for no absolute paths}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# v Checking for only portable paths}}\end{kframe}
\begin{kframe}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# -- Summary of fertile checks ----------------------------------------------- fertile 0.0.0.9028 --}}\end{kframe}
\begin{kframe}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# v Reproducibility checks passed: 2}}\end{kframe}
\end{knitrout}

@@

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# -- Analysis of reproducibility for project\_miceps -------------------------- fertile 0.0.0.9028 --}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# --\ \  Packages referenced in source code ------------------------------------ fertile 0.0.0.9028 --}}\begin{verbatim}
## # A tibble: 9 x 3
##   package       N used_in                    
##   <chr>     <int> <chr>                      
## 1 broom         1 project_miceps/analysis.Rmd
## 2 dplyr         1 project_miceps/analysis.Rmd
## 3 ggplot2       1 project_miceps/analysis.Rmd
## 4 purrr         1 project_miceps/analysis.Rmd
## 5 readr         1 project_miceps/analysis.Rmd
## 6 rmarkdown     1 project_miceps/analysis.Rmd
## 7 skimr         1 project_miceps/analysis.Rmd
## 8 stargazer     1 project_miceps/analysis.Rmd
## 9 tidyr         1 project_miceps/analysis.Rmd
\end{verbatim}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# --\ \  Files present in directory -------------------------------------------- fertile 0.0.0.9028 --}}\begin{verbatim}
## # A tibble: 9 x 4
##   file               ext        size mime                                       
##   <fs::path>         <chr> <fs::byt> <chr>                                      
## 1 Estrogen_Receptor~ docx     10.97K application/vnd.openxmlformats-officedocum~
## 2 citrate_v_time.png png     188.68K image/png                                  
## 3 proteins_v_time.p~ png     379.22K image/png                                  
## 4 Blot_data_updated~ csv      14.43K text/csv                                   
## 5 CS_data_redone.csv csv       7.39K text/csv                                   
## 6 mice.csv           csv      14.33K text/csv                                   
## 7 README.md          md           39 text/markdown                              
## 8 miceps.Rproj       Rproj       204 text/rstudio                               
## 9 analysis.Rmd       Rmd       4.94K text/x-markdown
\end{verbatim}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# --\ \  Suggestions for moving files ------------------------------------------ fertile 0.0.0.9028 --}}\begin{verbatim}
## # A tibble: 7 x 3
##   path_rel           dir_rel    cmd                                             
##   <fs::path>         <fs::path> <chr>                                           
## 1 Blot_data_updated~ data-raw   file_move('project_miceps/Blot_data_updated.csv~
## 2 CS_data_redone.csv data-raw   file_move('project_miceps/CS_data_redone.csv', ~
## 3 Estrogen_Receptor~ inst/other file_move('project_miceps/Estrogen_Receptors.do~
## 4 analysis.Rmd       vignettes  file_move('project_miceps/analysis.Rmd', fs::di~
## 5 citrate_v_time.png inst/image file_move('project_miceps/citrate_v_time.png', ~
## 6 mice.csv           data-raw   file_move('project_miceps/mice.csv', fs::dir_cr~
## 7 proteins_v_time.p~ inst/image file_move('project_miceps/proteins_v_time.png',~
\end{verbatim}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# --\ \  Problematic paths logged ---------------------------------------------- fertile 0.0.0.9028 --}}\begin{verbatim}
## NULL
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{log_report}\hlstd{()}
\end{alltt}
\begin{verbatim}
## # A tibble: 5 x 4
##   path         path_abs                             func     timestamp          
##   <chr>        <chr>                                <chr>    <dttm>             
## 1 package:pur~ <NA>                                 base::l~ 2020-10-11 15:10:40
## 2 package:for~ <NA>                                 base::l~ 2020-10-11 15:10:40
## 3 Seed Before  <NA>                                 14       2020-10-11 15:10:40
## 4 project_mic~ /Users/audreybertin/Documents/ferti~ readr::~ 2020-10-11 15:10:40
## 5 Seed After   <NA>                                 28       2020-10-11 15:10:40
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{fertile}\hlopt{::}\hlstd{read_csv}
\end{alltt}
\begin{verbatim}
## function(file, ...) {
## 
##   if (interactive_log_on()) {
##     if (Sys.getenv("FERTILE_RENDER_MODE") == TRUE){
##       log_push('Seed Before', .Random.seed[2])
##     }
## 
##     log_push(file, "readr::read_csv")
## 
##     check_path_safe(file, ... = "readr::read_csv")
## 
##     data <- readr::read_csv(file, ...)
## 
##     if (Sys.getenv("FERTILE_RENDER_MODE") == TRUE){
##       log_push('Seed After', .Random.seed[2])
##     }
## 
##     return (data)
##   }
## }
## <bytecode: 0x7f9a68cb9468>
## <environment: namespace:fertile>
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{proj_dir}
\end{alltt}
\begin{verbatim}
## [1] "project_miceps"
\end{verbatim}
\begin{alltt}
\hlstd{fs}\hlopt{::}\hlkwd{dir_ls}\hlstd{(proj_dir)} \hlopt{%>%} \hlkwd{head}\hlstd{(}\hlnum{3}\hlstd{)}
\end{alltt}
\begin{verbatim}
## project_miceps/Blot_data_updated.csv   project_miceps/CS_data_redone.csv      
## project_miceps/Estrogen_Receptors.docx
\end{verbatim}
\begin{alltt}
\hlstd{temp_dir} \hlkwb{<-} \hlkwd{sandbox}\hlstd{(proj_dir)}
\hlstd{temp_dir}
\end{alltt}
\begin{verbatim}
## /var/folders/v6/f62qz88s0sd5n3yqw9d8sb300000gn/T/Rtmpz372mQ/project_miceps
\end{verbatim}
\begin{alltt}
\hlstd{fs}\hlopt{::}\hlkwd{dir_ls}\hlstd{(temp_dir)} \hlopt{%>%} \hlkwd{head}\hlstd{(}\hlnum{3}\hlstd{)}
\end{alltt}
\begin{verbatim}
## /var/folders/v6/f62qz88s0sd5n3yqw9d8sb300000gn/T/Rtmpz372mQ/project_miceps/Blot_data_updated.csv
## /var/folders/v6/f62qz88s0sd5n3yqw9d8sb300000gn/T/Rtmpz372mQ/project_miceps/CS_data_redone.csv
## /var/folders/v6/f62qz88s0sd5n3yqw9d8sb300000gn/T/Rtmpz372mQ/project_miceps/Estrogen_Receptors.docx
\end{verbatim}
\end{kframe}
\end{knitrout}
